%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Tyler Cash} % Your name
\address{0411~$\cdot$~319~$\cdot$~513 \\ contact@tylercash.xyz \\ \href{https://github.com/Tyler-Cash}{\color{blue}{Github}}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}


    \begin{rSubsection}{Macquarie Group}{June 2018 - Present}{Junior Software Developer}{Sydney, NSW}
    \item Worked with a team to deliver an automated infrastructure build process for a Hadoop datalake
    \item Implemented sophisticated data extraction and manipulation processes with Java, Python and Bash
    \item Supported datalake users write SQL queries and also with Spark jobs in Java
    \item Automated manual administrative tasks to empower team to spend more time on developement tasks
    \end{rSubsection}
    
    \begin{rSubsection}{Macquarie University - Human Sciences IT}{March 2018 - June 2018}{Software Intern}{North Ryde, NSW}
    \item Automated process saving the business 250 hours a month.
    \item Wrote Javascript to integrate with preexisting service.
    \end{rSubsection}
    
    \begin{rSubsection}{Propeller Aero}{November 2017 - March 2018}{Software Intern}{Surry Hills, NSW}
    \item Increased the company's revenue by implementing features which allowed the sales team to expand current customer's usage of the product.
    \item Refactored large pre-existing systems into microservices that ran in Docker containers. 
    \item Deployed Docker images using Terraform and Kubernetes so that all infrastructure deployment was automated.
    \item Improved test coverage so that the CI/CD system was more useful and informative. This allowed my team to find and correct bugs more quickly.
    \item Translated repository from Python2 to Python3.
    \end{rSubsection}
    
    \end{rSection}
    
    %----------------------------------------------------------------------------------------
    %	EDUCATION SECTION
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Education}
    
        {\bf Macquarie University, NSW} \hfill {\em 2018} \\ 
        B.Sc. major in Computing with a minor in Software Engineering and Software Technology\\
        
        \end{rSection}
    
    %----------------------------------------------------------------------------------------
    %	PROJECTS SECTION
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Personal Projects}
    
    %------------------------------------------------
   
   
    \begin{rSubsection}{Home lab}{}{}{}{}{}
    \item Tier 1 hypervisor across 3 different nodes
    \item Kubernetes deployed so that there's an easy way to deploy internal services with a self hosted Gitlab instance 
    \end{rSubsection}
   
    \begin{rSubsection}{Resume}{Always updated!}{\href{https://github.com/Tyler-Cash/Latex-Resume}{\color{blue}{Github Repository}}}{}
    \item Resume written in LaTeX.
    \item Compiled to PDF using a docker CI/CD system which automatically adds a release on commit (\href{https://github.com/Tyler-Cash/Latex-Resume/releases}{\color{blue}{link}})
    \end{rSubsection}
    
    \end{rSection}
    
    %----------------------------------------------------------------------------------------
    %	TECHNICAL STRENGTHS SECTION
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Technical Strengths}
    
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Languages (Strongest to weakest) & Python, Java, C\#, Groovy, JavaScript, Scala, C/C++, XSLT \\
    Protocols \& APIs & XML, JSON \\
    Databases & MySQL, PostgreSQL, SQLite3 \\
    Skills & Big data, CI/CD, Linux, Networking, Geodetics \\
    Tools & Git, SVN, Codeship, Terraform
    \end{tabular}
    
    \end{rSection}
    
    \end{document}
